Total Score

### 2023-02-08 src/MSAtotal_scores.Rmd
finalized bar chart

```{r data viz}
## read in weighted criteria sheet
weighted_criteria <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "wtd_criteria_Owen") %>% 
  unite("msa_state", city_msa:state, sep = ", ")

# read in cbsa data with full names
score_tidy <- weighted_criteria %>% 
  pivot_longer(cols = c("WT_real_estate":"WT_climRisk"), # selecting criteria cols
               names_to = "criteria",
               values_to = "criteria_score") %>% 
 filter(msa_state != "Portland, ME") %>%  # removing portland (negative number)
  group_by(cbsa)

ggplot(data = score_tidy, aes(y = reorder(msa_state, FINAL_owen_SCORE), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  theme_light() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord Policy"))

>>>>

```{r client data viz}
## read in weighted criteria sheet
client_weighted_criteria <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "wtd_criteria_Owen") %>% 
  unite("msa_state", city_msa:state, sep = ", ")

# read in cbsa data with full names
score_tidy <- client_weighted_criteria %>% 
  pivot_longer(cols = c("WT_real_estate":"WT_climRisk"), # selecting criteria cols
               names_to = "criteria",
               values_to = "criteria_score") %>% 
 filter(msa_state != "Portland, ME") %>%  # removing portland (negative number)
  group_by(cbsa)

tiff(filename = "wt_criteria_client_chart.tiff", width = 8, height = 6, units = "in", res = 300)
ggplot(data = score_tidy, aes(y = reorder(msa_state, FINAL_owen_SCORE), x = criteria_score)) +
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score",
       y = " ",
       title = "Client") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Solar IRR", "Real Estate", "Landlord Policy")) +
  scale_x_continuous(limits = c(0, 0.7), expand = c(0,0), breaks=seq(0, 0.7, 0.1))
dev.off()
```

```{r}
## read in weighted criteria sheet
student_weighted_criteria <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "wtd_criteria_stud") %>% 
  unite("msa_state", city_msa:state, sep = ", ")

# read in cbsa data with full names
score_tidy2 <- student_weighted_criteria %>% 
  pivot_longer(cols = c("WT_real_estate":"WT_climRisk"), # selecting criteria cols
               names_to = "criteria",
               values_to = "criteria_score") %>% 
# filter(msa_state != "Portland, ME") %>%  # removing portland (negative number)
  group_by(cbsa)

tiff(filename = "wt_criteria_student_chart.tiff", width = 8, height = 6, units = "in", res = 300)
ggplot(data = score_tidy2, aes(y = reorder(msa_state, FINAL_st_score), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score",
       y = " ",
       title = "Student") +
  theme_bw() +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("palevioletred1","#FDB462",  "gold", "#44AA99", "dodgerblue4", "#BC80BD"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Solar IRR", "Real Estate", "Health Impacts")) +
  scale_x_continuous(limits = c(0, 0.8), expand = c(0,0), breaks=seq(0, 0.8, 0.1))
dev.off()
```
